Including EW and mixed QCD-EW corrections into PDF fits

### 2020-03-25 paper/paper.tex
adding analysis and some placeholders

SC

For datasets in 3.1qed (+DY2), compute pure NLO QCD (born) vs NLO QCD + NLO EW (dressed) FKtables and:\\
- compute data/prediction plots\\
- compute chi2\\

@@

C.S. is supported by the European Research Council under the European Unions Horizon 2020 research and innovation Programme (grant agreement no. 740006).

>>>>

In Table~\ref{table:chi2} we show the $\chi^2$ values for datasets..., using the NNPDF3.1 NLO luxQED set.

In Figure~\ref{fig:datacomparison} we present the data prediction comparison for the equivalent setup presented in Table~\ref{table:chi2}.

\begin{table}
    \centering
    \begin{tabular}{l|c|cc}
        \multicolumn{1}{l}{} &  & \multicolumn{2}{c}{$\chi^{2}/n_{{\rm data}}$}\tabularnewline
        \hline
        Dataset & $n_{{\rm data}}$ & QCD & QCD+EW\tabularnewline
        \hline
        ATLAS HM DY 7 TeV & 13 & 1.151 & 1.036\tabularnewline
        \hline
        ATLAS $\sigma_{tt}^{{\rm tot}}$ & 3 & 2.549 & 3.271\tabularnewline
        \hline
        CMS $\sigma_{tt}^{{\rm tot}}$ & 3 & 0.986 & 1.654\tabularnewline
        \hline
    \end{tabular}
    \caption{$\chi^2$ values for NNPDF3.1 NLO luxQED.}
    \label{table:chi2}
\end{table}

\begin{figure}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs0_datanorm_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs1_datanorm_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_plot_fancy_dataspecs_0}
    \includegraphics[width=0.5\textwidth]{plots/matched_datasets_from_dataspecs2_datanorm_plot_fancy_dataspecs_0}
    \caption{Data prediction comparison plots.}
    \label{fig:datacomparison}
\end{figure}

@@

S.C. and C.S. are supported by the European Research Council under the European Unions Horizon 2020 research and innovation Programme (grant agreement no. 740006).
